A Comparison of Graph Processing Systems

### 2020-09-22 documentation/paper/sections/preliminiaries.tex
Conclusion angefangen

The output of PageRank is a percentage for each vertex. This percentage, called the PageRank of the vertex, is the probability of arriving at this vertex when starting at a random vertex and then following random edges.
With a small probability, the damping factor, a jump is made to a completely random vertex instead of following a edge.
The PageRank can be calculated by iterating
\begin{equation*}
	\operatorname{PR}(v_i) = \frac{1 - d}{|V|} + d \sum_{v_j \in N^-(v_i)} \frac{\operatorname{PR}(v_j)}{\operatorname{deg^+}(v_j)}
\end{equation*}
for all edges $v_i \in V$.
$d$ is the damping factor, $deg^+(v)$ is the number of outgoing edges the vertex $v$ has and $N^-(v)$ denotes the set of vertices that have edges to vertex $v$.

>>>>

The output of PageRank is a percentage for each vertex. This percentage, called the PageRank of the vertex, is the probability of arriving at this vertex when starting at a random vertex and then following random edges.
With a small probability, the damping factor, a jump is made to a completely random vertex instead of following a edge.
The PageRank can be calculated by iterating
\begin{equation*}
	\operatorname{PR}(v_i) = \frac{1 - d}{|V|} + d \sum_{v_j \in \operatorname{N^-}(v_i)} \frac{\operatorname{PR}(v_j)}{\operatorname{deg^+}(v_j)}
\end{equation*}
for all edges $v_i \in V$.
$d$ is the damping factor, $\operatorname{deg^+}(v)$ is the number of outgoing edges the vertex $v$ has and $\operatorname{N^-}(v)$ denotes the set of vertices that have edges to vertex $v$.
